### 2012-04-24 docs/unit_tests/unit_tests.tex
add note about BDS in 3d

  This test initializes a Gaussian density field (no other scalar
  quantities are used) and a uniform velocity field in any one of the
  coordinate directions.  The Gaussian profile is advected through
  the period domain exactly once and the error in the density profile
  (L2 norm) is computed.  The driver for this problem does this 
  for every dimension twice (once with a positive velocity and once
  with a negative velocity).  After all coordinate directions are 
  tested, the norms are compared to ensure that the error does
  not show any directional bias.

>>>>

  This test initializes a Gaussian density field (no other scalar
  quantities are used) and a uniform velocity field in any one of the
  coordinate directions.  The Gaussian profile is advected through the
  period domain exactly once and the error in the density profile (L2
  norm) is computed.  The driver for this problem does this for every
  dimension twice (once with a positive velocity and once with a
  negative velocity), and loops over all advection methods ({\tt
  ppm\_type = 0,1,2} and {\tt bds\_type = 1}).  After all coordinate
  directions are tested, the norms are compared to ensure that the
  error does not show any directional bias.

  Note: the BDS advection method does not guarantee that the error be
  independent of the advection direction---small differences can
  arise.  What's happening here is that within each cell BDS is trying
  to define a tri-linear profile for rho subject to the constrants in
  the BDS paper~\cite{bds3d} (constraints 1 and 2 on p.\ 2044 after eq. 3.4).  We
  do not solve the L2 minimization problem exactly so we iterate up to
  3 times using a simple heuristic algorithm designed to work toward
  the constraint.  The iteration will give different results depending
  on orientation since we work through the corners in arbitrary order.
